\documentclass{report}

% Packages
\usepackage[utf8]{inputenc}

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{pgfplots}
\newtheorem{Example}{Example}
\usepackage[T1]{fontenc}    % Encodage des polices
\usepackage[english,french]{babel} % Langue du document
\usepackage{subcaption}
\usepackage{hyperref}       % Pour les liens hypertextes
\usepackage{listings}
\usepackage{xcolor}

% Titre du rapport
\title{The Discovery of an  Algebraic structure}
\author{ASSIGBE Komi \\ RAHOUTI Chahid .}
\date{\today}

\begin{document}

\maketitle
\newpage
\tableofcontents

\newpage

\section{Introduction}

\subsection{Definition}
    What is an Algebraic structure? An algebraic structure consists of a nonempty set A (called the underlying set, carrier set or domain), a collection of operations on A (typically binary operations such as addition and multiplication), and a finite set of identities, known as axioms, that these operations must satisfy.

    Among the multiples algebraic structures, we can name:
    \begin{itemize}
        \item Group
        \item Ring
        \item Field
        \item Vector space
                \item .....
            \end{itemize}

        \begin{Example}
            A simple example of a group for 
            addition is the additive group 
            of integers $ (\mathbb{Z}, +) $ 
            satisfies the following properties 
            for any $ a, b, c \in \mathbb{Z} $:
            \begin{itemize}
                \item Closure under the addition operation: $ a + b $ is an integer.
                \item Associativity: $ (a + b) + c = a + (b + c) $.
                \item Existence of the identity element: There exists an element $ 0 \in \mathbb{Z} $ such that $ a + 0 = a $ for every $ a \in \mathbb{Z} $.
                \item Existence of inverses: For each element $ a \in \mathbb{Z} $, there exists an element $ -a \in \mathbb{Z} $ such that $ a + (-a) = 0 $.
                \item Commutativity: $ a + b = b + a $ for every $ a, b \in \mathbb{Z} $.
            \end{itemize}
        These properties make $ (\mathbb{Z}, +) $ a fundamental example of an additive group.
            
        \end{Example}   

        \section{Objective}
        Our problem is a mathematical problem known 
        as data detection on structured surfaces or 
        varieties. When presented with a dataset $V$ 
        defined on such structured surfaces, the challenge 
        arises in determining whether there exists a 
        discernible algebraic pattern within the data. 
        Essentially, it's about investigating whether 
        there are underlying mathematical relationships 
        or structures governing the given dataset. 
        This problem is crucial in various fields 
        such as algebraic geometry and data analysis, 
        where understanding these structures aids in 
        making predictions or drawing meaningful 
        conclusions from the data. Thus, the goal 
        is to identify and characterize the algebraic
        properties inherent in the dataset for further
        analysis and interpretation.\\

        \begin{tikzpicture}
        \begin{axis}[
            axis lines = middle,
            xlabel = $x$,
            ylabel = {$f(x)$},
            domain=-3:3,
            samples=100,
        ]

        \addplot[blue, thick]{x^3 + x^2};
        \addplot[red, mark = *, only marks] coordinates {(-1,0) (1,2)};
        \addplot[green, mark = *, only marks] coordinates {(2,12)};
        \addplot[dashed, gray] coordinates {(-1,0) (1,2) (2,12)};

        \end{axis}
        \end{tikzpicture}


        \textbf{We have two main sub-objectives to address:}

        \begin{enumerate}
            \item Setting  points in a space or a surface, we want to know if it is possible to define a binary operation on these points such that they form a group. In other words, 
            we are going to Transform the axioms of a group to a loss function, that we will minimize to find a binary operation that satisfies these axioms.
                \item Is it possible to find a function  $f$ which can map binary operations (especially $\oplus$ and $\odot$) defined on $V$ to a binary operation defined on $\mathbb{R}$ such that the group axioms are satisfied
            \end{enumerate}



        \section{First sub-objective}
            Let's take an example of a group structure.
            let consider a surface $M \in \mathbb{R}^{n \times n}$
            Like, M =  $\begin{bmatrix}
                \vdots & \vdots & \vdots &\vdots \\
                x_{1} & x_{2} & \cdots & x_{n} \\
                \vdots & \vdots & \vdots &\vdots \\
            \end{bmatrix}$   with $x_{i} \in \mathbb{R}^{d}$ \\
    The question is if we consider M as a group structure, it is possible to find a binary operation ($\circ$) on M such that M is following these group axioms.
    \begin{enumerate}
        \item $\exists e \in M, \forall x \in M, e \circ x = x \circ e = x$
        \item $\forall{} x,y \in{} M, x \circ y = y \circ x$
        \item $\forall x,y,z \in M, (x \circ y) \circ z = x \circ (y \circ z)$
        \item $\forall x \in M, \exists -x \in M, x \circ -x = -x \circ x = e$
    \end{enumerate}

% Contenu de la section 2

\section{Second sub-Objective}
	let consider a set of points  $ V $ and let  $ f: R \rightarrow V $ a one-to-one
	function from $R$ into a codomain $V$. We define two binary operations $\oplus$ and $\odot$ on $V$ as follows:
    $$ x \oplus y = f(f^{-1}(x) + f^{-1}(y)) $$
    $$ \alpha \odot x = f(  \alpha.f^{-1}(x)) $$
	The question is if we consider $V$ as a group 
    structure, it is possible to find a binary 
    operation ($\oplus$) and ($\otimes $) on $V$ and a function f 
    such that this relations is satisfying.
    \begin{Example}[Trivial Example]
        Let f be a function from $R$ to $Vect{(e_1)}$ such that $f(x) = x.e_1$.
        we have $f^{-1}(x) = \lambda$.
            we take x and y in $vect{(e_1)}$, we have \\
            $x\oplus y = f(f^{-1}(x) + f^{-1}(y)) = x + y$ \\
            $\alpha \odot x = f(f^{-1}(x) * \alpha) = \alpha x$ 
    \end{Example}
    \begin{Example}[Non-Trivial Example]
        Let $\beta$ be any positive real number and let $f: \mathbb{R} \rightarrow \mathbb{R}_{+}^{*}$be
        defined by $f(x)=(1 / \beta) e^x$. Then $f$ is a one-to-one
        function from $\mathbb{R}$ onto the set of positive real numbers, 
        and $f^{-1}(x)=\ln (\beta x)$ for $x>0$. we would define vector 
        addition and scalar multiplication by
        $$
        x \oplus y=\frac{1}{\beta} e^{\ln (\beta x)+\ln (\beta y)}=\beta x y
        $$ 
        
        $$
        \alpha \odot x=\frac{1}{\beta} e^{\alpha \ln (\beta x)}=\beta^{\alpha-1} x^\alpha.
        $$ 
    \end{Example}
	
\section{Tools}
    To address these objectives, we leverage
    the Pytorch library in Python using Neural Networks Learning to find the optimal parameters that minimize the loss function.\\
    We are also going to use also Git to share Code and collaborate on the project.\\ 
    We will also use slack for communication and sharing information.\\

    For Example, \textbf{for the fist sub-objective, we can define the losses as follows}:

    \begin{enumerate}
        \item Existence of the identity element:  \[
            L_1(\theta) = \sum_{v \in V} (e_{\text{obs}} - e_{\text{pred}})^2
            \]
        \item Commutativity:
        \[
        L_2(\theta) = \sum_{(x, y) \in V \times V} (x \oplus y - y \oplus x)^2
        \]
        \item Associativity:
        \[
        L_3(\theta) = \sum_{(x, y, z) \in V \times V \times V} ((x \oplus y) \oplus z - x \oplus (y \oplus z))^2
        \]
        \item Existence of inverses:
        \[
        L_4(\theta) = \sum_{x \in V} (-x_{\text{obs}} + (-x_{\text{pred}}))^2
        \] 
    \end{enumerate}
    
    Here, $\theta$ represents the parameters of our model.
    These functions $L_i(\theta)$ measure the discrepancies
    between the observed and predicted values for each group 
    axiom, where $i = 1, 2, 3, 4$. By minimizing these functions
    $L_i(\theta)$, we aim to adjust our model to be as close as
    possible to the real data, ensuring that our algebraic 
    structure accurately satisfies the group axioms. 

    $$
    L(\theta) = \min_{\theta} L_1(\theta) + L_2(\theta) + L_3(\theta) + L_4(\theta)
    $$


    This function $L(\theta)$ represents the sum of losses 
    associated with each group axiom. By minimizing 
    this function $L(\theta)$, we aim to adjust our model so
    that it optimally satisfies the four group axioms, 
    ensuring the accuracy and consistency of our 
    algebraic structure with respect to the provided data.\\


    \textbf{For the second sub-objective, we can define the losses as follows:}
    Here are the two losses for the second approach
  \begin{enumerate}
    \item Loss for vector addition:
    \[
    L_1(\theta) = \sum_{(x, y) \in V \times V} \left\lVert x \oplus y - \left(f(f^{-1}(x)) + f(f^{-1}(y))\right) \right\rVert^2
    \]
    \item Loss for scalar multiplication:
    \[
    L_2(\theta) = \sum_{(\alpha, x) \in \mathbb{R} \times V} \left\lVert \alpha \odot x - f(\alpha \cdot f^{-1}(x)) \right\rVert^2
    \]
\end{enumerate}

Function $L(\theta)$, the sum of these two functions:
\[
L(\theta) = L_1(\theta) + L_2(\theta)
\]
Here, $\theta$ represents the parameters of 
our model. These functions $L_1(\theta)$ and
$L_2(\theta)$ measure the discrepancies between 
the observed and predicted values for vector addition 
and scalar multiplication operations, respectively. 
By minimizing these functions, we aim to adjust our 
model to accurately represent the algebraic structure 
present in the dataset. \\  


\section{Application}
Many differential equations encountered 
in solving have parametric solutions.
Thus, to find the solution for each 
parameter, this often requires 
numerous calculations. To optimize 
computation and storage times, we 
define an algebraic structure 
whereby, if we compute the solution 
for parameters $\lambda_1$ and $ \lambda_2 $,
we can deduce $\lambda_3$ ...
\begin{Example}
    Consider the general form of a first-order linear ODE with a parameter $\lambda$:
    
    \[
    \frac{dy}{dx} + \lambda y = 0
    \]
    
    The solution to this differential 
    equation depends on the parameter
    $\lambda$, the solution to this ODE is given by:
    
    \[
    y(x) = C e^{-\lambda x}
    \]
    where $C$ is the constant of integration.
    The solution on $y(0)=1$ is given by:
    $y(x) = e^{-\lambda x}$
    

\begin{tikzpicture}
\begin{axis}[
    axis lines = middle,
    xlabel = $x$,
    ylabel = {$y(x)$},
    domain=0:3,
    samples=100,
    legend pos=outer north east
]

\addplot[blue, thick]{exp(-0.5*x)}; \addlegendentry{$\lambda = 0.5$}
\addplot[red, thick]{exp(-3*x)}; \addlegendentry{$\lambda = 3$}
\addplot[green, thick]{exp(-7*x)}; \addlegendentry{$\lambda = 7$}

\end{axis}
\end{tikzpicture}


In this example, the parameter $\lambda$ affects the behavior of the solution function $y(x)$. Different values of $\lambda$ lead to different solutions, each with its own characteristic behavior. Thus, the solution is a function with a parameter $\lambda$.
\end{Example}

\section{Conclusion}
this project provides a comprehensive 
exploration of algebraic structures and
their relevance in data analysis, 
offering insights into how these 
structures can be effectively applied 
to detect patterns and derive meaningful
conclusions from datasets. Through Python 
implementation and testing, the project 
demonstrates practical approaches to 
optimize algebraic structures for 
improved accuracy and performance 
in various applications
    
\end{document}